\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Added the MSE MNISt section

The digit 1 of MNIST dataset consists of $7877$ grayscale images of handwritten digits [@lecun2010]. Before further analysis, PCA was used to preprocess the data, where the first $10$ principal components, explaining 83% of the total variation, were selected. The objective is to select the best NLDR layout, representing the structure of the digit 1 data in $10\text{-}D$ with default (hyper-)parameters.

>>>>

The digit 1 of the MNIST dataset consists of $7877$ grayscale images of handwritten digits [@lecun2010]. Before further analysis, PCA was used to preprocess the data, where the first $10$ principal components, explaining 83% of the total variation, were selected. The objective is to select a reasonable NLDR layout, representing the non-linear sub-clustering structure of the digit 1 dataset in $10\text{-}D$.

The MSE for different $a_1$ using tSNE, UMAP, PHATE, PaCMAP, and TriMAP with default (hyper-)parameter setting (@fig-mnist-mse) were calculated. It is found that tSNE provide the most reasonable representation for the digit 1 dataset, showing universally best (@fig-mnist-mse).

### 2024-09-06 paper.tex
Added the MSE MNISt section

The digit 1 of MNIST dataset consists of \(7877\) grayscale images of
handwritten digits \citep{lecun2010}. Before further analysis, PCA was
used to preprocess the data, where the first \(10\) principal
components, explaining 83\% of the total variation, were selected. The
objective is to select the best NLDR layout, representing the structure
of the digit 1 data in \(10\text{-}D\) with default (hyper-)parameters.

>>>>

The digit 1 of the MNIST dataset consists of \(7877\) grayscale images
of handwritten digits \citep{lecun2010}. Before further analysis, PCA
was used to preprocess the data, where the first \(10\) principal
components, explaining 83\% of the total variation, were selected. The
objective is to select a reasonable NLDR layout, representing the
non-linear sub-clustering structure of the digit 1 dataset in
\(10\text{-}D\).

The MSE for different \(a_1\) using tSNE, UMAP, PHATE, PaCMAP, and
TriMAP with default (hyper-)parameter setting
(Figure~\ref{fig-mnist-mse}) were calculated. It is found that tSNE
provide the most reasonable representation for the digit 1 dataset,
showing universally best (Figure~\ref{fig-mnist-mse}).
